Hidden Talents Multiverse Analysis

### 2021-02-07 README.Rmd
fix typo
trying to fix the README table

-   [OSF project](https://osf.io/6r95z/)
-   [Original preregistration](https://osf.io/d2gz6/)
-   [Overview of measures](https://osf.io/5kawy/), which fully describes what was collected (including measures not used/analyzed in this project). Specific variable codebooks for the current project are contained in this repository (see Codeboooks below).
-   [Final preregistration](https://osf.io/4vsnz/) which also contains a preliminary write-up of the Methods for an eventual publication
-   [Secondary analysis plan - set 1](https://osf.io/7fu35/)
-   [Secondary analysis plan - set 2](https://osf.io/wcauf/)

@@

file_list %>% 
  select(dir,script, input, output) %>% 
  gt(id = "one", rowname_col = "row", groupname_col = "dir") %>% 
  fmt_markdown(columns = T)
```

>>>>

-   [OSF project](https://osf.io/6r95z/)
-   [Original preregistration](https://osf.io/d2gz6/)
-   [Overview of measures](https://osf.io/5kawy/), which fully describes what was collected (including measures not used/analyzed in this project). Variable codebooks for the current project are contained in this repository (see Codebooks below).
-   [Final preregistration](https://osf.io/4vsnz/) which also contains a preliminary write-up of the Methods for an eventual publication
-   [Secondary analysis plan - set 1](https://osf.io/7fu35/)
-   [Secondary analysis plan - set 2](https://osf.io/wcauf/)

@@

file_list %>% 
  select(dir,script, input, output) %>% 
  gt(id = "one", rowname_col = "row", groupname_col = "dir") %>% 
  fmt_markdown(columns = T) %>% 
  gt::as_raw_html()
```
